The core transcriptome of the mammal placenta

### 2016-08-12 manuscript/manuscript.Rnw
add changes for elsarticle

%\documentclass[english,12pt]{article}
\documentclass[doublespacing]{bmcart_dla}
\usepackage{fontspec}
\setmainfont{FreeSans}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSans}
\setmathsf{FreeSans}
\setmathtt{FreeSans}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
\usepackage{url}
% \usepackage{fancyhdr}
\usepackage{graphicx}
% \usepackage[bf]{caption}
\usepackage{rotating}
\usepackage{wrapfig}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{wrapfig}
% \usepackage{txfonts}
%\usepackage[plain]{fancyref}
\usepackage{acronym}
\usepackage{array}
\usepackage{dcolumn}
\usepackage{adjustbox}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{amsmath}
\usepackage{sansmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
% \usepackage[noblocks,auth-sc]{authblk}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue]{hyperref}
%\usepackage[hyperfigures,bookmarks,colorlinks,citecolor=black,filecolor=black,linkcolor=black,urlcolor=black]{hyperref}
% Floats at end for journals
\usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
\renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
\renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
\usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
\renewcommand\cite[1]{\autocite{#1}}
% \pagestyle{fancy}

@@

\begin{document}
\raggedright

@@

  \parttitle{Conclusions} A diverse array of genes are differentially
  expressed and are likely to play a role in the anatomical
  variability of the placenta in the placentas of mammalian lineages.
  Furthermore, multiple genes which are associated with pre-eclampsia
  (\textit{CRH}, \textit{ADAM12}, \textit{KISS1}, \textit{PAPPA},
  \textit{IL1RL1}, and \textit{PLAC1}) show increased expression on
  the human lineage. Still, using the strictest filtering strategy
  we find a core set of only
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  genes is essential for the proper functioning of the placenta in all
  species analyzed.

@@

\begin{table}
  \begin{tabular}{c >{\raggedright \centering}p{1in} c c c}
    \toprule
    Species                       & Common Name & Gestation (days) & \multicolumn{1}{p{1in}}{\centering Average Litter Size}  & Source \\
    \midrule
    \textit{Ateles fusciceps}     & Spider monkey & 224 & 1 & \citet{Ernest2003:lifehistorycharacteristicsofplacental}\\
    \textit{Bos taurus}           & Cow & 278 & 1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Canis familiaris}     & Dog & 61 & 4 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Dasypus novemcinctus} & Nine-banded Armadillo & 150 & 4 & \citet{Smith1984:amazingarmadillo} \\
    \textit{Equus caballus}       & Horse & 336 & 1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation}\\
    \textit{Loxodonta africana}   & African savanna elephant & 644 & 1 & \citet{Ernest2003:lifehistorycharacteristicsofplacental}\\
    \textit{Homo sapiens}         & Human & 270 & 1.1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Monodelphis domestica}& Gray short-tailed opossum & 15 & 7.1 & \citet{Harder.ea1993:Gestationandplacentationin} \\
    \textit{Mus musculus}         & Mouse & 20 & 6.1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Spalax galili}   & Blind mole rat from Upper Galilee & 28-42 & 4 & \citet{Nevo1997:mosiacevolutionofsubterranianmammals} \\
    \textit{Ovis aries}           & Domestic sheep & 151 & 1.35 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Pan paniscus}         & Bonobo & 223 & 1 & \citet{Ernest2003:lifehistorycharacteristicsofplacental} \\
    \textit{Spalax carmeli}       & Blind mole rat from northern Israel & 28-42 & 4 & \citet{Nevo1997:mosiacevolutionofsubterranianmammals}\\
    \textit{Sus scrofa}           & Domestic pig (Duroc) & 114 & 5.8 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \bottomrule
  \end{tabular}
  \caption{Gestational periods in days and average liter sizes for studied species.}
  \label{tab:gestational_periods}
\end{table}

@@

popViewport(1)
grid.text(c("A","B","C","D"),
          x=unit(c(0,0.5,0,0.5),"npc"),y=unit(c(1,1,0.5,0.5),"npc"),
          just=c("left","top"),
          gp=gpar(fontsize="48")
          )
@ 
\caption{\genetreeexplanation{(A) \textit{PSG1}, (B) \textit{CTSL}, (C) \textit{PRSS16}, and (D) \textit{PAG2}}}
\label{fig:pag2_prss16_ctsl_psg_evolution_tree}
\end{figure}

@@

\section{Conclusion}

@@

\begin{backmatter}
  \section*{Competing interests}
  The authors declare that they have no competing interests.

>>>>

%\documentclass[english,12pt]{article}
\documentclass[5p]{elsarticle_dla}
\usepackage{fontspec}
\setmainfont{FreeSerif}
\setsansfont{FreeSans}
\setmonofont{FreeMono}
\setmathrm{FreeSerif}
\setmathsf{FreeSans}
\setmathtt{FreeSerif}
%\usepackage[letterpaper,left=1in,right=1in,top=1in,bottom=1in,headheight=14pt]{geometry}
\usepackage[letterpaper]{geometry}
%\usepackage{url}
\usepackage{graphicx}
%\usepackage{rotating}
%\usepackage{wrapfig}
\usepackage{booktabs}
%\usepackage{float}
\usepackage{multirow}
%\usepackage{setspace}
\usepackage{acronym}
\usepackage{array}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage[backend=biber,natbib=true,hyperref=true,citestyle=numeric-comp,style=nature,autocite=inline]{biblatex}
\addbibresource{references.bib}
\usepackage[hyperfigures,bookmarks,colorlinks,linkcolor=black,urlcolor=black,citecolor=blue]{hyperref}
% Floats at end for journals
% \usepackage[nolists,figuresfirst,nomarkers,heads]{endfloat}
% \renewcommand{\efloatseparator}{\mbox{}}
%\AtBeginFigures{\newpage \renewcommand{\efloatseparator}{\mbox{}}\section*{Figure Legends}}
%\AtBeginTables{\newpage \section*{Tables}\renewcommand{\efloatseparator}{\mbox{}}}
% \renewcommand{\includegraphics}[2][]{}
\usepackage[nomargin,inline,draft]{fixme}
\newcommand{\DLA}[1]{\textcolor{red}{\fxnote{DLA: #1}}}
\newcommand{\DEW}[1]{\textcolor{purple}{\fxnote{DEW: #1}}}
% \usepackage[x11names,svgnames]{xcolor}
% \usepackage{texshade}
% \usepackage{tikz}
\usepackage{nameref}
\usepackage{xspace}
% this package will stretch the font slightly if necessary.
% \usepackage{microtype}
\usepackage{zref-xr,zref-user}
\zxrsetup{toltxlabel}
\zexternaldocument*{supplemental_material}
\usepackage[capitalize]{cleveref}
% \newenvironment{narrow}[2]{%
%   \begin{list}{}{%
%       \setlength{\topsep}{0pt}%
%       \setlength{\leftmargin}{#1}%
%       \setlength{\rightmargin}{#2}%
%       \setlength{\listparindent}{\parindent}%
%       \setlength{\itemindent}{\parindent}%
%       \setlength{\parsep}{\parskip}}%
%   \item[]}{\end{list}}
% \def\newblock{\hskip}
% \newenvironment{paperquote}{%
%   \begin{quote}%
%      \it
%   }%
%   {\end{quote}}
% \renewcommand{\textfraction}{0.15}
% \renewcommand{\topfraction}{0.85}
% \renewcommand{\bottomfraction}{0.65}
% \renewcommand{\floatpagefraction}{0.60}
%\renewcommand{\baselinestretch}{1.8}
% \newenvironment{enumerate*}%
%   {\begin{enumerate}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{enumerate}}
% \newenvironment{itemize*}%
%   {\begin{itemize}%
%     \setlength{\itemsep}{0pt}%
%     \setlength{\parskip}{0pt}}%
%   {\end{itemize}}
% \setcounter{tocdepth}{3}
% \oddsidemargin 0.0in 
% \textwidth 6in
% \raggedbottom
% \clubpenalty = 10000
% \widowpenalty = 10000
% set a large emergency stretch to avoid issues with overfull boxes
% \setlength{\emergencystretch}{20em}
% make the afill smaller
% \renewcommand\Affilfont{\itshape\small}
%\renewcommand\cite[1]{\autocite{#1}}
%\renewcommand\citet[1]{\textcite{#1}}
% \pagestyle{fancy}

@@

\begin{document}
% \raggedright

@@

  \textbf{Conclusions} A diverse array of genes are differentially
  expressed and are likely to play a role in the anatomical
  variability of the placenta in the placentas of mammalian lineages.
  Furthermore, multiple genes which are associated with pre-eclampsia
  (\textit{CRH}, \textit{ADAM12}, \textit{KISS1}, \textit{PAPPA},
  \textit{IL1RL1}, and \textit{PLAC1}) show increased expression on
  the human lineage. Still, using the strictest filtering strategy
  we find a core set of only
  \Sexpr{core.placenta.transcriptome.long[,length(unique(human_name))]}
  genes is essential for the proper functioning of the placenta in all
  species analyzed.

@@

\begin{table}
  \small
  \begin{tabular}{>{\raggedright }p{0.7in}
                  >{\raggedright }p{0.7in}
                  c c 
                  p{0.65in}}
    \toprule
    {\centering Species  }                     & {\centering Common Name }& 
       \multicolumn{1}{p{0.43in}}{\raggedright \centering Gestation (days)} & 
       \multicolumn{1}{p{0.3in}}{\raggedright \centering Litter Size}  & Source \\
    \midrule
    \textit{Ateles fusciceps}     & Spider monkey & 224 & 1 & \citet{Ernest2003:lifehistorycharacteristicsofplacental}\\
    \textit{Bos taurus}           & Cow & 278 & 1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Canis familiaris}     & Dog & 61 & 4 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Dasypus novemcinctus} & Nine-banded Armadillo & 150 & 4 & \citet{Smith1984:amazingarmadillo} \\
    \textit{Equus caballus}       & Horse & 336 & 1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation}\\
    \textit{Loxodonta africana}   & African savanna elephant & 644 & 1 & \citet{Ernest2003:lifehistorycharacteristicsofplacental}\\
    \textit{Homo sapiens}         & Human & 270 & 1.1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Monodelphis domestica}& Gray short-tailed opossum & 15 & 7.1 & \citet{Harder.ea1993:Gestationandplacentationin} \\
    \textit{Mus musculus}         & Mouse & 20 & 6.1 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Spalax galili}   & Blind mole rat from Upper Galilee & 28-42 & 4 & \citet{Nevo1997:mosiacevolutionofsubterranianmammals} \\
    \textit{Ovis aries}           & Domestic sheep & 151 & 1.35 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \textit{Pan paniscus}         & Bonobo & 223 & 1 & \citet{Ernest2003:lifehistorycharacteristicsofplacental} \\
    \textit{Spalax carmeli}       & Blind mole rat from northern Israel & 28-42 & 4 & \citet{Nevo1997:mosiacevolutionofsubterranianmammals}\\
    \textit{Sus scrofa}           & Domestic pig (Duroc) & 114 & 5.8 & \citet{Kiltie1982:intraspecificvariationmammaliangestation} \\
    \bottomrule
  \end{tabular}
  \caption{Gestational periods in days and average liter sizes for studied species.}
  \label{tab:gestational_periods}
\end{table}

@@

popViewport(1)
grid.text(c("A","B","C","D"),
          x=unit(c(0,0.5,0,0.5),"npc"),y=unit(c(1,1,0.5,0.5),"npc"),
          just=c("left","top"),
          gp=gpar(fontsize="48")
          )
@ 
\caption{\genetreeexplanation{(A) \textit{PSG1}, (B) \textit{CTSL}, (C) \textit{PRSS16}, and (D) \textit{PAG2}}}
\label{fig:pag2_prss16_ctsl_psg_evolution_tree}
\end{figure*}

@@

\subsection{Conclusion}

@@

%\begin{backmatter}
  \section*{Competing interests}
  The authors declare that they have no competing interests.
